Gravitational Lens Recovery with \Glass: How to measure the mass profile and shape of a lens

### 2013-06-13 limits/ms.tex
Fixed missing figure reference.

With the stellar mass lower bound, the improvement of the reconstruction
quality shown in \figref{Test reconstructions} is quite dramatic for the
steepest mock galaxies (AC and BC). This is because these models are dominated
by stars in the inner region. The other two galaxies are unaffected because the
models were already well modeled by the dark matter alone.

>>>>

With the stellar mass lower bound, the improvement of the reconstruction
quality shown in \figref{main results} is quite dramatic for the
steepest mock galaxies (AC and BC). This is because these models are dominated
by stars in the inner region. The other two galaxies are unaffected because the
models were already well modeled by the dark matter alone.
